On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-02-01 docs/mvfits_paper/mvf.tex
updating ref responses

Here, the labels $\ell$ and $m$ are polar and azimuthal eigenvalues of \tk{'s} angular equations, where units of $M_i=1$ (e.g. the initial mass of the \bbh{} system), and $c=1$.

@@

In the third line of \eqn{hrd}, we represent $h$ in terms of \textit{spherical} harmonic multipoles.

@@

In the \eob{} formalism, $h\LM$ is modeled such that, after its peak (near merger), the effective functional form reduces (asymptotically) to \eqn{hrd}'s second line \cite{Cotesta:2018fcv, Buonanno:2000ef, Bohe:2016gbl,Pan:2013rra, Bohe:2016gbl, Nagar:2018zoe}.

@@

Only where $\jf \cw\lmn=0$ do $_{-2}S\lmn( 0,\theta,\phi) = {_{-2}}Y_{\ell m}\theta,\phi)$, which makes equating the spherical and spheroidal harmonics approximate at best for general values of $\jf \cw\lmn$.

@@

In that setting, it is demonstrated that \qnm{} frequencies correlate with the morphology of each $h\LM$ in not only \rd{}, but also merger and late inspiral, as is implied by the source's causal connectedness pre and post merger.

@@

is the \textit{pseudo-inverse} \cite{Moore1920,Penrose:1955} of $\hatU$.

@@

This forward greedy process ends when the model accuracy, or changes thereof, passes a previously specified threshold.

@@

  \caption{A positive (forward) greedy algorithm, \pgreedy{}. Note that a required input, $\mathcal{A}$, is a function that takes in a list of basis symbols, and outputs an estimator of fit error. In this setting, $\mathcal{A}$ is assumed to have access to peripheral information, such as the training data.}

>>>>

Here, the labels $\ell$ and $m$ are polar and azimuthal eigenvalues of \tk{'s} angular equations, where total mass and the speed of light are set to unity (i.e. $M=c=1$).

@@

Note that barred indices, namely $\bar{\ell}$ and $\bar{m}$, will refer to \textit{spherical} harmonics, leaving the unbarred indices to refer to the spheroidals.
In the third line of \eqn{hrd}, we represent $h$ in terms of {spherical} harmonic multipoles.

@@

In the \eob{} formalism, $h\LM$ is modeled such that, after its peak (near merger), the effective functional form reduces (asymptotically) to \eqn{hrd}'s second line \cite{Cotesta:2018fcv, Buonanno:2000ef,
Bohe:2016gbl,Pan:2013rra, Bohe:2016gbl, Nagar:2018zoe}.

@@

Only where $\jf \cw\lmn=0$ do $_{-2}S\lmn( 0,\theta,\phi) = {_{-2}}Y_{\ell m}(\theta,\phi)$, which makes equating the spherical and spheroidal harmonics approximate at best for general values of $\jf \cw\lmn$.

@@

In that setting, it is demonstrated that \qnm{} frequencies are linked to the amplitude and phase of each $h\LM$ in not only \rd{}, but also merger and late inspiral, as is implied by the source's causal connectedness pre and post merger.

@@

is the \textit{pseudo-inverse} \cite{Moore1920,Penrose:1955} of $\hatU$, which exists if $\hatU^{*} \hatU$ is nonsingular.

@@

This forward greedy process ends when the model accuracy, and/or changes thereof, passes a previously specified threshold.

@@

  \caption{A positive (forward) greedy algorithm, \pgreedy{}. Note that a required input, $\mathcal{A}$, is a function that takes in a list of basis symbols, and outputs an estimator of fit error (e.g. L2 norm). In this setting, $\mathcal{A}$ is assumed to have access to peripheral information, such as the training data.}
